---
title: "hejpakken"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hejpakken}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
Repository link: https://github.com/rforbiodatascience24/group_29_package
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=4, 
  fig.align = "center",
  fig.asp = 0.618
)
```

```{r setup}
library("hejpakken")
```

## Description of hejpakken package

This package called hejpakken is used for creating functions that can help automation of converting a DNA sequence into a sequence of amino acids. This represents the different steps in protein synthesis which is a part of the central dogma.

## Functions of hejpakken

In hejpakken there are 5 build-in functions:

### 1. Nucleotide sequence sampler

The nucleotide sequence sampler samples a selected number of DNA bases into a DNA sequence. As an example, here is a sequence of 24 bases:

```{r}
#| echo: true
nucleotide_sequence_sampler(24)
```

### 2. Convert T to U

The converter of T to U changes DNA sequences into RNA sequences. This is done by converting "T" to "U" in strings. An example is written here:

```{r}
#| echo: true
DNA_sequence <- "ACGTTGCA" 
convert_T_to_U(DNA_sequence)
```

### 3. Extract codons

The code extract function splits one string representing a RNA sequence into several different codons. For each three letters (nucleotides) in the input string, a new string containing three letters (codons) will be formed. An example is presented here:

```{r}
#| echo: true
RNA_sequence <- "ACGUUGCA"
extract_codons(RNA_sequence)
```

### 4. Codon to Amino Acids

This function takes a list of strings containing three letters representing nucleotides and return one string containing letters representing amino acids. Here an example is presented:

```{r}
#| echo: true
codons <- c("ACG","UUG")
codon_to_AA(codons)
```

### 5. Amino acid frequency plot

The amino acid count of insulin is illustrated with the function below:

```{r}
#| echo: true
INS <- "MALWMRLLPLLALLALWGPDPAAAFVNQHLCGSHLVEALYLVCGERGFFYTPKTRREAEDLQVGQVELGGGPGAGSLQPLALEGSLQKRGIVEQCCTSICSLYQLENYCN"

amino_acid_plot(INS)
```

### Merging all the functions

The functions can be used all together, where you can illustrate the frequency of different amino acids, based on random base sampling. This can illustrate that if the base is sampled randomly, then some amino acids are of higher likability than others.

```{r}
#| echo: true
#150 random bases are sampled
dna_bases <- nucleotide_sequence_sampler(150)
#Bases are converted to RNA string
rna_bases <- convert_T_to_U(dna_bases)
#The rna bases are converted into codons
codons <- extract_codons(rna_bases)
#The codons are translated into an amino acid sequence
aa_sequence <- codon_to_AA(codons)
#The amino acids are illustrated in a count barplot
p1 <- amino_acid_plot(aa_sequence)
```

The plot has now been saved under the variable `p1`

## Further development of hejpakken

Other functions that could be included could be to categorize the amino acids based on chemical properties like their hydrophobic hydrophilic characteristics , acidic/basic conditions, polarity and aliphatic/aromatic properties.

In function five, the two packages were added as dependencies by using `@importFrom package function` tag to load the ggplot2 and stringr packages.

It's a good idea to limit the number of dependencies of the package, since they can increase the risk of compatibility issues, slow down package installation. It can increase the potential for errors if one of the dependencies updates or changes functionality.

The differences between adding an `@importFrom package function` tag to a function description compared to using `package::function()` is that `@importFrom package function` adds the function to your package’s namespace as a formal dependency, loading the external package whenever your package is loaded. In contrast, `package::function()` does not add it to the namespace, loading the package only when needed, which keeps your package lighter.
