---
title: "hejpakken"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hejpakken}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hejpakken)
```

## Description

## Functions of hejpakken

In hejpakken there are 5 builtin functions:

1.  Nucleotide_sequence_sampler

2.  Amino_acid_plot

### Nucleotide sequence sampler

The nucleotide sequence sampler samples a selected number of DNA bases into a DNA sequence.

As an example, here is a sequence of 24 bases:

```{r}
example_sequence_24 <- nucleotide_sequence_sampler(24)
print(example_sequence_24)
```

### Amino acid frequency plot

The amino acid plot illustrates the count of each amino acids within an amino acid sequence in a barchart

The amino acid count of insulin is illustrated with the function below:

```{r}
INS <- "MALWMRLLPLLALLALWGPDPAAAFVNQHLCGSHLVEALYLVCGERGFFYTPKTRREAEDLQVGQVELGGGPGAGSLQPLALEGSLQKRGIVEQCCTSICSLYQLENYCN"

amino_acid_plot(INS)
```

## Further development of hejpakken
